\documentclass{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{hyperref}

\title{Plantronics Voyager 510 cheat sheet}
\author{Kenyon Ralph}

\begin{document}

\maketitle

\section{Lights}
\label{sec:lights}

\begin{itemize}
\item Red, red flashing slow: charging.
\item Blue with occasional quick flashes: fully charged.
\item Blue flashing slow: headset on.
\item Blue flashing fast: call connected.
\item Red flashing: low battery.
\end{itemize}

\section{Functions}
\label{sec:functions}

\begin{itemize}
\item Pairing
  \begin{enumerate}
  \item Simultaneously hold the Call Control Button and the Volume
    Increase Button until the light flashes red and blue.
  \item Passkey: 0000
  \end{enumerate}
\item Reset headset: simultaneously hold Volume Decrease Button and
  Power/Mute Button for 3 s.
\item Power/Mute Button
  \begin{enumerate}
  \item Hold 3 seconds: power on/off.
  \item During a call: press for $<$ 1 s to mute the microphone. When
    muted, headset will sound 2 tones every 30 seconds. Press again to
    unmute.
  \end{enumerate}
\item Call Control Button
  \begin{enumerate}
  \item During a call on headset: press for $<$ 1 s to end call. Hold
    until second tone to transfer call to handset.
  \item During a call on handset: press for $<$ 1 s to transfer to
    headset.
  \item Incoming call: press for $<$ 1 s to answer call. Hold until
    second tone to reject call.
  \item Idle: until second tone for voice dialing. Quickly
    double-click to redial last number.
  \end{enumerate}
\item Volume Adjust Buttons
  \begin{enumerate}
  \item During a call on headset: adjust headset speaker volume.
  \end{enumerate}
\end{itemize}

\section{See also}
\label{sec:see-also}

\begin{itemize}
\item \url{http://bindoo.blogspot.com/2010/03/lights-on-plantronics-voyager-510.html}
\item \url{http://www.plantronics.com/north_america/en_US/products/office/wireless-headsets/voyager-510}
\end{itemize}

\end{document}
